HBCC - ACC - STG - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-01-03 cmc-rnaseq-de/HBCC_ACC-STG_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
patch script with new md ver

# Get RNASeq QCmetadata
METADATA_QC_ID = 'syn16816488' 
ALL_USED_IDs = METADATA_QC_ID
metadata = downloadFile_version(METADATA_QC_ID, version = 14) %>%
  dplyr::select(`Individual_ID`, Institution, `Reported_Gender`, Sex, Ethnicity, ageOfDeath, `PMI_(in_hours)`, Dx, 
                Sample_RNA_ID, one_of('rnaSeq_isolation:RIN',
                                      'rnaSeq_dissection:Brain_Region',
                                      'rnaSeq_isolation:RNA_Isolation_Batch',
                                      'rnaSeq_report:Library_Batch', 
                                      'rnaSeq_report:Flowcell_Batch', 'rnaSeq_report:Exclude?',
                                      'rnaSeq_report:Mapped_Reads',
                                      'rnaSeq_report:Intragenic_Rate','rnaSeq_report:Intronic_Rate',
                                      'rnaSeq_report:Intergenic_Rate','rnaSeq_report:Genes_Detected',
                                      'rnaSeq_report:Expression_Profiling_Efficiency',
                                      'rnaSeq_report:rRNA_Rate',
                                      'rnaSeq_report:Total_Reads', 'rnaSeq_report:Percent_Aligned',
                                      'rnaSeq_report:Transcripts_Detected')) %>% 
  dplyr::filter(Institution %in% c("NIMH-HBCC")) %>% 
  dplyr::filter(`rnaSeq_dissection:Brain_Region` %in% c("ACC","STG"))

>>>>

# Get RNASeq QCmetadata
METADATA_QC_ID = 'syn16816488' 
ALL_USED_IDs = METADATA_QC_ID
metadata = downloadFile_version(METADATA_QC_ID, version = 15) %>%
  dplyr::select(`Individual_ID`, Institution, `Reported_Gender`, Sex, Ethnicity, ageOfDeath, `PMI_(in_hours)`, Dx, 
                Sample_RNA_ID, one_of('rnaSeq_isolation:RIN',
                                      'rnaSeq_dissection:Brain_Region',
                                      'rnaSeq_isolation:RNA_Isolation_Batch',
                                      'rnaSeq_report:Library_Batch', 
                                      'rnaSeq_report:Flowcell_Batch', 'rnaSeq_report:Exclude?',
                                      'rnaSeq_report:Mapped_Reads',
                                      'rnaSeq_report:Intragenic_Rate','rnaSeq_report:Intronic_Rate',
                                      'rnaSeq_report:Intergenic_Rate','rnaSeq_report:Genes_Detected',
                                      'rnaSeq_report:Expression_Profiling_Efficiency',
                                      'rnaSeq_report:rRNA_Rate',
                                      'rnaSeq_report:Total_Reads', 'rnaSeq_report:Percent_Aligned',
                                      'rnaSeq_report:Transcripts_Detected')) %>% 
  dplyr::filter(Institution %in% c("NIMH-HBCC")) %>% 
  dplyr::filter(`rnaSeq_dissection:Brain_Region` %in% c("ACC","STG"))
